Data description

### 2019-08-27 paper_results/Data/data-description.Rmd
Formatting readme

---
title: "Data description"
author: "Gallagher, Frisoli, and Luby"
date: "August 6, 2019"
output:
  pdf_document
---

@@

```{r invis-setup, echo = FALSE}
devtools::load_all("~/courtsports")
library(knitr)
library(kableExtra)
library(broom)
library(tidyverse)
```

@@

```{r summary-gs-players, echo = FALSE}
gs_players %>% summary() %>% t() %>% 
  kable(., format = "latex",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in \\texttt{gs\\_players}.",
      escape = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

@@

```{r summary-gs-pbp, echo = FALSE}
gs_pbp %>% summary() %>% t() %>% 
  kable(., format = "latex",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in \\texttt{gs\\_pbp}.",
      escape = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

@@

```{r summary-gs-partial, echo = FALSE}
gs_partial %>% summary() %>% t() %>% 
  kable(., format = "latex",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in \\texttt{gs\\_partial}.",
      escape = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

@@

```{r summary-gs-partial-players, echo = FALSE}
gs_partial_players %>% summary() %>% t() %>% 
  kable(., format = "latex",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in \\texttt{gs\\_partial\\_players}.",
      escape = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

>>>>

---
title: "Data description"
author: "Gallagher, Frisoli, and Luby"
date: "September 5, 2019"
output:
  html_document
---

@@

```{r invis-setup, echo = FALSE, warning = FALSE, message = FALSE}
devtools::load_all("~/courtsports")
library(knitr)
library(kableExtra)
library(broom)
library(tidyverse)
```

@@

```{r summary-gs-players, echo = FALSE}
gs_players %>% summary() %>% t() %>% 
  kable(., format = "html",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in gs_players.",
      escape = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r summary-gs-pbp, echo = FALSE}
gs_pbp %>% summary() %>% t() %>% 
  kable(., format = "html",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in gs_pbp.",
      escape = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

@@

```{r summary-gs-partial, echo = FALSE}
gs_partial %>% summary() %>% t() %>% 
  kable(., format = "html",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in gs_partial.",
      escape = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) #%>%
  ##kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

@@

```{r summary-gs-partial-players, echo = FALSE}
gs_partial_players %>% summary() %>% t() %>% 
  kable(., format = "html",  
      booktabs = TRUE, digits = 1, 
      caption = "Summary of covariates in gs_partial_players}.",
      escape = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
 ## kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```
